Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-08-02 Manuscript/SS_GAM.tex
Run pipeline

\usepackage{tikz}
\usepackage{pgfplots}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrllllll}
  \hline
 & p & bglm\_spline\_de & blasso\_spline & cosso & acosso & mgcv & SB\_GAM \\ 
  \hline
1 & 4.00 & 0.90 (0.01) & 0.90 (0.01) & 0.73 (0.09) & 0.71 (0.13) & 0.90 (0.01) & 0.82 (0.04) \\ 
  2 & 10.00 & 0.90 (0.01) & 0.88 (0.01) & 0.67 (0.16) & 0.76 (0.04) & 0.90 (0.01) & 0.82 (0.04) \\ 
  3 & 50.00 & 0.88 (0.01) & 0.81 (0.05) & 0.43 (0.19) & 0.54 (0.19) & 0.86 (0.02) & 0.81 (0.07) \\ 
  4 & 200.00 & 0.73 (0.10) & 0.60 (0.08) & 0.39 (0.17) & 0.45 (0.19) & NaN (NA) & 0.81 (0.05) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measure over for binomial outcome over 50 iterations} 
\label{tab:gaus}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrllllll}
  \hline
 & p & bglm\_spline\_de & blasso\_spline & cosso & acosso & mgcv & SB\_GAM \\ 
  \hline
1 & 4.00 & 0.94 (0.01) & 0.89 (0.04) & 0.90 (0.02) & 0.90 (0.02) & 0.94 (0.01) & 0.93 (0.01) \\ 
  2 & 10.00 & 0.93 (0.01) & 0.87 (0.03) & 0.87 (0.03) & 0.85 (0.03) & 0.92 (0.04) & 0.92 (0.01) \\ 
  3 & 50.00 & 0.92 (0.01) & 0.87 (0.02) & 0.83 (0.02) & 0.83 (0.02) & 0.76 (0.04) & 0.92 (0.01) \\ 
  4 & 200.00 & 0.88 (0.01) & 0.86 (0.02) & 0.81 (0.06) & 0.81 (0.08) & NaN (NA) & 0.92 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measure over for binomial outcome over 50 iterations} 
\label{tab:bin_auc}
\end{table}

To evaluate the predictive performance of the models, \(R^2\) for
Gaussian model, area under the curve (AUC) are calculated for binomial
model, averaging across 50 simulations. The results are tabulated in
Table \ref{tab:gaus}, \ref{tab:bin_auc}.\footnote{is it better to
  provide a box plot or a table.}

@@

For the binomial outcome shown in Figure 1, we can see that the proposed
models are consistently performed better than COSSO and adaptive COSSO.
Mgcv slightly outperforms the proposed models in low dimension
settings(p = 4, 10), but suffers from overfitting in medium dimension
setting (p=50). In addition, in the high-dimension setting (p=200), mgcv
could not make prediction due to the p \textgreater{} n problem. Among
the proposed models, we see that there is modest difference between the
models that shares the same indicator variable('\_spline' models) and or
not sharing indicator variable (modles), where the not sharing indicator
variable models have slightly edge over indicator sharing model.
Moreover, the mixture double exponential model and lasso model perform
substaintially better in the medium and high settings. For the remaining
two outcomes, the results shows similar trends, where mixture double
exponential model and ss lasso model are recommended for use.

\%are calculated to assess out-of-sample estimation accuracy,

\%We also calculated the area under the curve (AUC) of the receiver
operating characteristic curve for \(y_{new}\). We will also visually
display the estimated smooth function with the smooth function of truth
to compare if the models can infer the smooth function correctly,
despite the prediction accuracy.

\%When constructing the smooth function of each variables, we constructs
the natural cubic spline with degree of freedom 25. In other words, the
design matrix of each smooth function will have 26 columns. The total
number of columns for \(p=4, 10, 50\) is \(105, 261, 1301\)
respectively, where intercept is kept in the model when fitting. The
\(p=50\) can mimic the high dimensional setting as the design matrix are
in high-dimensional setting (\(p >> n\))

\%We benchmark the performance of the proposed methods with the state of
art GAM package \texttt{mgcv}{[}TODO: add citation{]}. In the future
steps, we will compare our proposed model with other high dimensional
GAM applications.

@@

Overall, the proposed priors outperforms the state-of-art GAM model
\texttt{mgcv} when the dimensionality is low, median, and high. The
proposed priors predicts better than \texttt{mgcv} and infers better of
the underlying smooth function. Most importantly, \texttt{mgcv} is
infeasible in the high dimensional setting, i.e.~when \(p=50\) where the
number of parameters are greater than the sample size.

\hypertarget{prediction-performace}{%
\paragraph{Prediction Performace}\label{prediction-performace}}

The prediction performance is tabulated in the table below for AUC and
Supplementary tables for MSE and misclassification rate. In summary, the
proposed Bayesian models outperforms the benchmark model \texttt{mgcv}
regardless the choice of prior or fitting algorithm. The models with
IRLS fitting algorithm give slightly better performance than the the
model with cyclic coordinate descent algorithm. The advantage diminishes
in the high dimensional setting (p=50). This is possible because the SS
normal spline prior provides a more smooth solution, which would work
well in a low to median dimension setting. However, in the high
dimensional setting, there are not enough sparsity in the model, i.e.~SS
normal prior will provides a more complex model than necessary. This is
confirmed with the visualization in the following section.

\hypertarget{visualization}{%
\paragraph{Visualization}\label{visualization}}

We plot the estimated smooth functions of the four active variables for
the 100 simulation iterations, along with the `true' smooth function.
Across different settings of predictors, the patterns look similar.
First of all, in all the settings, \texttt{mgcv} tends to provide more
extreme models, where in the graphs the smooth function have much higher
bound than the true smooth function. Rarely the estimated smooth
function from \texttt{mgcv} matches with the true smooth function. In
comparison, the proposed method can interpolate the shape of the true
smooth function. However, different priors and fitting algorithms have
different advantages. For example, in Figure 1, we see that the SS
normal distribution have problem with the tail of the smooth function,
especially obvious in the estimations of the variable \emph{x4}.
However, it would have less sparse solutions, which is more likely to
accurately interpolate the smooth function especially when the shape is
complicated (see variable \emph{x2}). On the contrary, the SS double
exponential prior model encourages sparse solutions, which can sometime
omit active predictors.

\hypertarget{real-data-analysis}{%
\section{Real Data Analysis}\label{real-data-analysis}}

>>>>

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rrllllll}
  \hline
 & p & bglm\_spline\_de & blasso\_spline & cosso & acosso & mgcv & SB\_GAM \\ 
  \hline
1 & 4.00 & 0.90 (0.01) & 0.90 (0.01) & 0.73 (0.09) & 0.71 (0.13) & 0.90 (0.01) & 0.82 (0.04) \\ 
  2 & 10.00 & 0.90 (0.01) & 0.88 (0.01) & 0.67 (0.16) & 0.76 (0.04) & 0.90 (0.01) & 0.82 (0.04) \\ 
  3 & 50.00 & 0.88 (0.01) & 0.81 (0.05) & 0.43 (0.19) & 0.54 (0.19) & 0.86 (0.02) & 0.81 (0.07) \\ 
  4 & 200.00 & 0.73 (0.10) & 0.60 (0.08) & 0.39 (0.17) & 0.45 (0.19) & NaN (NA) & 0.81 (0.05) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample $R^2$ measure for Gaussian outcomes over 50 iterations} 
\label{tab:gaus}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrllllll}
  \hline
 & p & bglm\_spline\_de & blasso\_spline & cosso & acosso & mgcv & SB\_GAM \\ 
  \hline
1 & 4.00 & 0.94 (0.01) & 0.89 (0.04) & 0.90 (0.02) & 0.90 (0.02) & 0.94 (0.01) & 0.93 (0.01) \\ 
  2 & 10.00 & 0.93 (0.01) & 0.87 (0.03) & 0.87 (0.03) & 0.85 (0.03) & 0.92 (0.04) & 0.92 (0.01) \\ 
  3 & 50.00 & 0.92 (0.01) & 0.87 (0.02) & 0.83 (0.02) & 0.83 (0.02) & 0.76 (0.04) & 0.92 (0.01) \\ 
  4 & 200.00 & 0.88 (0.01) & 0.86 (0.02) & 0.81 (0.06) & 0.81 (0.08) & NaN (NA) & 0.92 (0.01) \\ 
   \hline
\end{tabular}
\caption{The average and standard deviation of the out-of-sample area under the curve measure for binomial outcomes over 50 iterations} 
\label{tab:bin_auc}
\end{table}

To evaluate the predictive performance of the models, the statistics
caluclated based on the testing dataset, \(R^2\) for Gaussian model,
area under the curve (AUC) for binomial model, are calculated averaging
across 50 simulations. The results are tabulated in Table
\ref{tab:gaus}, \ref{tab:bin_auc}.\footnote{is it better to provide a
  box plot or a table.}

@@

The predictive performances have a consistent pattern across the three
distributions of outcomes. Across all the scenarios, COSSO and adaptive
COSSO have the least favourable performance among the applicable methods
examined. To note, mgcv doesn't support high-dimensional analysis when
the number of coefficients are greater than the sample size. mgcv
predicts well when \(p\) is small or moderate (p = 4, 10), and
deteriorate when the number of predictors increase. Among the three
fast-computing Bayesian hierarchical models, the proposed models,
bglm\_spline\_de and blasso\_spline \footnote{need to change the name}
predicts better than SB-GAM when the dimension of are small, moderate,
and high. However, in the hyper high dimensional case, SB-GAM has better
performance. Among the proposed methods, bglm\_spline\_de performs
consistently better than blasso\_spline.

@@

\hypertarget{metabolomics-data-analysis}{%
\section{Metabolomics Data Analysis}\label{metabolomics-data-analysis}}

We use the proposed models BHAM-SSL to analyze metabolomics data from a
recently published study \footnote{TODO: add
  citation:\url{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0240764}}
on the association between metabolic biomarkers and weight loss. The
data contained 765 metaboliltes in baseline plasma collected from three
separate studies, profiled using liquid chromatography mass
spectrometry. Quality control and natural log transformation were
performed during metabolites data preparation. The outcome of interest
was percent change in insulin resistance, and hence modeled using a
Gaussian model adjusting for covariates including age, sex, race,
baseline clinical triglycerides, and percent change in weight over the
follow-up time period. 731 individuals were included in the initial
studies, and reduced to 315 after removing missing values. The
descriptive statistics were tabulated in Table \ref{tab:tbl_one}.

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{|p{2.14in}|p{1.44in}|p{1.56in}|p{1.75in}|p{1.39in}}

\caption{The descriptive statistics of the sample in the metabolomics data analysis stratified by studies\label{tab:tbl_one}}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Characteristic}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Overall,\ N\ =\ 315}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{CBD,\ N\ =\ 17}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{STRRIDEPD,\ N\ =\ 56}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM,\ N\ =\ 242}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} \\

\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-5}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Characteristic}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Overall,\ N\ =\ 315}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{CBD,\ N\ =\ 17}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{STRRIDEPD,\ N\ =\ 56}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM,\ N\ =\ 242}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} \\

\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-5}\endhead

\multicolumn{5}{!{\color[HTML]{FFFFFF}\vrule width 0pt}>{\raggedright}p{\dimexpr 8.28in+8\tabcolsep+4\arrayrulewidth}!{\color[HTML]{FFFFFF}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Median\ (IQR);\ n\ (\%)}}\fontsize{11}{11}\selectfont{\textsuperscript{\textcolor[HTML]{000000}{1}}}} \\

\endfoot

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{cov\_Age}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{56\ (51,\ 62)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{39\ (34,\ 47)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{60\ (55,\ 66)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{56\ (51,\ 62)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{cov\_Sex}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{F}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{188\ (60\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{14\ (82\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{33\ (59\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{141\ (58\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{M}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{127\ (40\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3\ (18\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{23\ (41\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{101\ (42\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{cov\_Race}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{AA}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{109\ (35\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{8\ (47\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9\ (16\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{92\ (38\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{EA}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{203\ (64\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{9\ (53\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{45\ (80\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{149\ (62\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{O}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3\ (1.0\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{0\ (0\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{2\ (3.6\%)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{1\ (0.4\%)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{cov\_Triglycerides\_Baseline}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{106\ (76,\ 154)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{118\ (91,\ 170)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{104\ (75,\ 150)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{106\ (76,\ 154)}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2.14in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{cov\_Weight\_PC}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.44in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{-7.6\ (-10.9,\ -5.6)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.56in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{-29.9\ (-37.0,\ -25.1)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{-3.1\ (-5.7,\ -0.6)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 1.39in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{-7.8\ (-10.8,\ -6.2)}}} \\

\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-5}

\end{longtable}
